\documentclass[10pt,letterpaper]{article}
\usepackage[parfill]{parskip}
\usepackage{array}
\usepackage{ifthen}
\usepackage{fontawesome}
\usepackage{hyperref}
\usepackage[usenames, dvipsnames]{color}
\pagestyle{empty}
\usepackage[default]{cantarell}
\usepackage[T1]{fontenc}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage{fancyhdr}

\newenvironment{mysection}[1]{ % 1 input argument - section name
  \medskip
  \MakeUppercase{\bf #1}
  \medskip
  \hrule
  \begin{list}{}{
      \setlength{\leftmargin}{1.5em}
    }
  \item[]
}{
  \end{list}
}


\definecolor{mygray}{gray}{0.6}
\begin{document}

\centerline{\MakeUppercase{\huge\bf Hebi Li}}
%% \centerline{PhD Candidate in Programming Languages \& Analysis}
\centerline{\textit{\textcolor{mygray}{1865 Long Rd, Unit A, Ames IA
      50010}}} \centerline{\faEnvelope ~ hebi@iastate.edu ~ | ~
  \faHome ~ lihebi.com ~ | ~ \faGithubSquare ~ lihebi}

\begin{mysection}{Education}
  \textbf{Iowa State University} \hfill \emph{Aug. 2014 - Aug 2019 (Expected)} \\
  \emph{PhD Student in Department of Computer Science}

  \textbf{University of Science and Technology of China}
  \hfill \emph{Aug. 2010 - Jun. 2014} \\
  \emph{B.E. in Electrical Engineering}
\end{mysection}

\begin{mysection}{Research Area}
  \begin{itemize}
  \item \textbf{Artificial Intelligence, Causality}
  \item \textbf{Natural Language Processing}
  \item \textbf{Programming Languages \& Analysis, Software Engineering}
  \end{itemize}
\end{mysection}

\begin{mysection}{Preferred Programming Skills}
  \begin{itemize}
  \item \textbf{Lisp \& Scheme dialects}: Racket, Common-Lisp, Emacs
    Lisp
  \item \textbf{C/C++}: familiar with LLVM/Clang, Boost
  \item \textbf{Python}: familiar with Tensorflow, BeautifulSoup
  \end{itemize}
\end{mysection}

\begin{mysection}{Research Projects}

  \textbf{NLP: Semantic metric for abstract doc summarization (Python,
    Tensorflow)} \hfill \emph{Spring 2018 - Present}
  \begin{itemize}
  \item Website \& Code: \url{https://github.com/lihebi/anti-rouge}
  \item Description: ROUGE is the de facto criterion for summarization
    research.  However, its two major drawbacks: 1. favors lexical
    similarity instead of semantic similarity 2. require a reference
    summary which may be expensive to obtain.  Therefore, we introduce
    a completely new end-to-end metric system for summary quality
    assessment by leveraging recently developed \textbf{deep sentence
      embedding}.

    We develop two \textbf{negative sample generation} approaches:
    \textit{random mutation} and \textit{cross-pairing}.  We apply and
    evaluate three sentence-embedding models: \textbf{Universal
      Sentence Encoder} by Google and \textbf{InferSent} by Facebook,
    and a vanilla word-embedding model \textbf{Grove}. We evaluate 3
    neural network architectures atop the embedding,
    \textbf{Fully-connected}, \textbf{CNN}, and \textbf{LSTM}.

  \item Publications: Hebi Li, Qi Xiao, Yinfei Yang, Forrest Sheng Bao,
      \textit{``End-to-end semantics-based summary quality assessment
        for single-document summarization''}, In submission to
      NAACL-2019.
  \end{itemize}
  
  \textbf{AI: Causal Discovery From High Dimensional Data (Python,
    Tensorflow)} \hfill \emph{Spring 2018 - Present}

  \begin{itemize}
  \item Description: Causality is believed by many to be the right way
    for Artificial General Intelligence. However, most causality
    research are done in low-dimensional data. We hence are interested
    in discovering causal relations embedded inside high dimensional
    data such as images and text. In particular, we are interested in
    mapping low-level raw pixels (micro variables) into high-level
    features (macro variables) that have explicit causal relations.
    The model is built atop \emph{Variational Causal Encoder (VAE)}.
  %% \item Publications: Hebi Li, Jin Tian, \textit{``Causal Discovery
  %%   From High Dimensional Data''}, In Progress.
  \end{itemize}
  
  \textbf{PL\&SE: Dynamic Program Analysis on Demand (C/C++, LLVM/Clang,
    Racket)} \hfill \emph{Summer 2015 - Spring 2018}

  \begin{itemize}
  \item Website: \url{https://helium.lihebi.com/}. V1 Code:
    \url{https://github.com/lihebi/Helium} (723 commits, 22k LOC
    C/C++). V2 Code: \url{https://github.com/lihebi/helium2} (143
    commits, 1.7k LOC Racket, 3k LOC C/C++).
  \item Description: Helium is a framework that debugs your program
    on-demand, preventing running time overhead by running just enough
    code. It generates a small partial program from the original big
    buggy program by performing data and control flow analysis and
    dynamically test to verify the bug.  It features a
    \textbf{syntactic patching algorithm} that find the extra code in
    addition to the user selection that is necessary for a valid
    partial program. It also features a \textbf{demand-driven context
      search algorithm} to find smaller partial programs that preserve
    a given program property.
  \item Implementation highlights: The framework uses
    \textbf{LLVM/Clang} framework as the underlying parser, and
    performs \textbf{AST modelling and manipulation}. \textbf{Program
      Generation} steps outputs partial programs, including
    \textbf{unit test generation} and \textbf{dynamic test data
      generation}. The framework is provided as \textbf{docker} image
    that is easy and ready to use. Partial program ASTs are visualized
    through \textbf{Graphviz} framework.
  \item Publications:
    \begin{itemize}
    \item Hebi Li, Wei Le, \textit{``Enabling Dynamic Analysis for
      Partial Programs Via Syntactic Patching''}, In submission.
    \item Hebi Li, Wei Le, \textit{``Demand-Driven Dynamic Analysis
      for Automatic Benchmark Building''}, In submission.
    \end{itemize}
  \end{itemize}

  \textbf{USTC Bachelor Thesis: Named Data Network} \hfill
  \emph{Summer 2013 - Summer 2014}

  Publications: Hebi Li, Xiaobin Tan \textit{``TreeSync: A Distributed
    Message Synchronization Algorithm Using Topology-Related Hierarchy
    over Named Data Network''}, USTC Thesis, 2014
\end{mysection}

\begin{mysection}{Open Source Projects}
  \begin{itemize}
  \item \textbf{hn.el (ELisp)}: A Hacker News Client for Emacs.
    \url{https://github.com/lihebi/hn.el}
  \item \textbf{simple-drill.el (Elisp)}: A Flashcard Program for
    Emacs. \url{https://github.com/lihebi/simple-drill.el}
  \item \textbf{smart-scholar.el (Elisp, Python)}: Download and manage
    bibs for CS conferences.
    \url{https://github.com/lihebi/smart-scholar.el}
  \end{itemize}
\end{mysection}

\begin{mysection}{Teaching Experience}
  TA in Network Programming, Applications, and Research Issues (ISU CS587)
  \hfill \emph{Spring 2019}
  
  TA in Advanced Design and Analysis of Algorithms (ISU CS511)
  \hfill \emph{Spring 2019}
  
  TA in Principles of Programming Languages (ISU CS342)
  \hfill \emph{Fall 2016, Fall 2017}

  TA in Introduction to Database System (ISU CS363)
  \hfill \emph{Fall 2014, Spring 2015}
\end{mysection}

%% \begin{mysection}{Awards}
%%   \textbf{Teaching Excellent Award} \hfill \emph{May 2017}
%% \end{mysection}

\end{document}
